### 2019-10-14 README.Rmd
update readme

The `taxize` tutorial is can be found at <https://ropensci.org/tutorials/taxize.html> and check out the taxize book <https://ropenscilabs.github.io/taxize-book/>

@@

## Tutorial

For more examples see the [tutorial][tut]

@@

[tut]: https://ropensci.org/tutorials/taxize.html
[coc]: https://github.com/ropensci/taxize/blob/master/CODE_OF_CONDUCT.md

>>>>

The taxize book => <https://taxize.dev>

@@

<br>

@@

[coc]: https://github.com/ropensci/taxize/blob/master/CODE_OF_CONDUCT.md
